2020-06-xx
Overheads:
1.Overheads from the invoking of real::malloc.(mallocation of pageInfo,cacheInfo,objectInfo,entryInHashMap)
a. too much number of invo
2.Overheads from too much memory access in the malloc function
3.Overheads in the handle access is higher after the program running a while(imbalance in the hashmap)
4.Start counting some information after second thread writing
5.shadow mapping?
Function:
1.how to output

The key to reduce overheads is to reduce cache miss(not necessary memory touch, small footprint, small cache invalidation, cache line align up).
And also reduce lock contention, use of lock and also use of CAS...


2020-07-18 Overheads:
Overheads
1. overheads from MemoryPool:
solution: add thread local cache , or try ptmalloc
2. overheads from hashmap-allocater, which is Real::malloc. that is super slow.
3. I guess samling is necessary, but with a smart sampling which do not influence it effects




2020-07-24 todo-lists:
1. confirm correctness, adujust format and content of analyze outputs.
2. deep analyze some applications and try to make improvements.
3. reduce overheads.
4. paper writing.

07-24 ------- 07-26: 1, 2
07-27 ------- 08-02: 2, 3
08-03 ------- 08-09: 3, 4
08-10 ------- 08-13: 3, 4

2020-08-03 todo-lists:
two main things: overheads and helping information in analyze results
    1. overheads: local allocate overheads, others not quite sure.
    2. helping information: what info needed in page centric level, fix helping for malloc call site
    3. deep analyze some applications and try to make improvements.
    4. paper writing.

08-03 ------- 08-09: 1
08-10 ------- 08-16: 1,2
08-17 ------- 08-23: 3,4
08-24 ------- 08-31: 3,4


overheads:
    1. remove any extra func calls: some if statement will bring big overheads since it may bring cache miss by access global variables.
    2. do sampling for some parts if it did not influence results.


08-11:
    1. if the dump does not need all detailed info, is it better to discard them in the diagnose objs.

08-12:
    1. I am not sure why the access num in page level is too small compared with previous version. It seems like better to use two
sampling for basic page and detail page info.